CITK - an architecture and examples of CUDA enabled ITK filters

### 2011-05-20 article/Article.tex
article update

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Richard Beare{$^1$}, Daniel Micevski, Chris Share\\Luke
  Parkinson, Phillip Ward, Wojtek Goscinski{$1$}, Mike Kuiper{$^2$}}
\authoraddress{{$^1$}Richard.Beare@monash.edu, Monash University, Melbourne, Australia\\
{$^2$}mike@vpac.org, Victorian Partnership for Advanced Computing, Melbourne, Australia.}

@@

This work was performed between late 2009 and early 2010 and is being
published as modifications to ITK 3.20. It is hoped that publication will
help inform more general development of GPU support in ITK 4.0 and
facilitate experimentation by users requiring functionality of 3.20 or
wishing to pursue CUDA based developments.
\end{abstract}

@@

\section{Installation and building}
\subsection{CUDA compiler and software development kit}
This framework requires CUDA 3.2 and the SDK. The {\em thrust} library
is also included in the examples to implement more complex components
of some sample filters.
\subsection{Patch ITK 3.20}
The code distributed with this article includes a patch to modify ITK 3.20. This can be applied as follows:

\begin{itemize}
\item \url{http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
\item extract
\item cd ITK-3.20
\item patch -p0 $<$ path/to/patch.3.20.0.dif 
\end{itemize}

@@

\subsection{Build and install modified ITK}
There are many options available when building ITK. This process has
been tested under Linux and there are a number of changes to defaults
required to avoid limitations to the CUDA development tools. 
\begin{itemize}
  \item Specify location of CUDA SDK.
  \item Turn off SSE options for VNL - advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
\end{itemize}

\subsection{Build examples}
The examples and tests are included in this package. The most up to
date version of the package can be found at \url{http://code.google.com/p/cuda-insight-toolkit/}.

@@

Finally, some positive performance results. These tests were carried
out using a Tesla T10 in a 16 core, 2261.051MHz, Intel L5520  Xeon:
\begin{itemize}
\item Performance improvement of 190 times observed with simple arithmetic, such as adding or subtracting constants from
  images. See {\em simple\_perf\_test.cxx} for details.
\item Image filtering with kernels, for example simple means, offer ??
  for 3d kernels, radius 10 voxels on images size $500 \times 500
  \times 500$. This is potentially interesting for applications
  requiring kernels of specific shape, because most accelerated CPU
  schemes can only implement a restricted range of shape kernels. The
  accelerated CPU scheme used in this test uses a box filtering
  approach that is limited to rectangular filters.
\end{itemize}

>>>>

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Richard Beare{$^1$}, Daniel Micevski, Chris Share\\Luke
  Parkinson, Phil Ward, Wojtek Goscinski{$1$}, Mike Kuiper{$^2$}}
\authoraddress{{$^1$}Richard.Beare@monash.edu, Monash University, Melbourne, Australia\\
{$^2$}mike@vpac.org, Victorian Partnership for Advanced Computing, Melbourne, Australia.}

@@

This work was performed between late 2009 and early 2010 and is being
published as modifications to ITK 3.20. It is hoped that publication will
help inform development of more general GPU support in ITK 4.0 and
facilitate experimentation by users requiring functionality of 3.20 or
wishing to pursue CUDA based developments.
\end{abstract}

@@

\section{Installation and building}
\subsection{CUDA compiler and software development kit}
This framework requires CUDA 3.2 and the SDK. The {\em thrust} library
is also included in the examples to implement more complex components
of some sample filters.
\subsection{Fetch this contribution from google code}
The source code is included with this article and is also available from google code:
\url{http://code.google.com/p/cuda-insight-toolkit/}. The patch for ITK is included.

\subsection{Patch ITK 3.20}
The code distributed with this article includes a patch to modify ITK
3.20, called {\em patch.3.20.0.dif}. This can be applied as follows:

\begin{itemize}
\item fetch \url{http://voxel.dl.sourceforge.net/sourceforge/itk/InsightToolkit-3.20.0.tar.gz}
\item extract
\item cd ITK-3.20
\item patch -p0 $<$ path/to/cuda-insight-toolkit/patch.3.20.0.dif
\end{itemize}

@@

\subsection{Build and install modified ITK}
There are many options available when building ITK. This process has
been tested under Linux and there are a number of changes to defaults
required to avoid limitations to the CUDA development tools. 
\begin{itemize}
  \item Specify location of CUDA SDK.
  \item Turn off SSE options for VNL - see advanced/VNL. This avoids errors caused by multiple inclusion of SSE files.
\end{itemize}

\subsection{Build examples}
The Examples subdirectory in the citk distribution includes a
CMakeFile for building all examples and running tests. Location of the
patched ITK, nvcc and CUDA SDK must be provided during configuration.

@@

Finally, some positive performance results. These tests were carried
out using a Tesla T10 in a 16 core, 2261.051MHz, Intel L5520  Xeon:
\begin{itemize}
\item Performance improvement of 190 times observed with simple arithmetic, such as adding or subtracting constants from
  images. See {\em simple\_perf\_test.cxx} for details.
\item Image filtering with kernels, for example simple means, offer 32
  times speedup for 3d kernels, radius 10 voxels on images size $500
  \times 500 \times 500$ and 50 times speedup for kernels radius
  20.. This is potentially interesting for applications requiring
  kernels of specific shape, because most accelerated CPU schemes can
  only implement a restricted range of shape kernels. Neither CPU nor
  GPU examples exploits redundancy in this test.
\end{itemize}
